---
title: "Compare Retention Time versus Sequence-specific
  retention calculator  using (F255744)"
author: "Christian Panse"
date: "2017-10-30"
bibliography:
  - NestLink.bib
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{3. Compare Predicted and Measured FlyCodes hydrophobicity values using  F255744.}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document
---

# Comparizon

To validate our Retention Time (RT) prediction in this vignette file, we compare the predicted hydrophobicity value using the `ssrc` method @pmid15238601 implemented in the 
`r CRANpkg("protViz")` package @protViz.

The following code snippet performs the comparison on the F255744 data.
The file contains amino acid sequences representing the designed FlyCodes.

```{r echo=TRUE, message=FALSE}
library(NestLink)
```

```{r fig.retina=1, fig.height=5, fig.width=5}
# load(url("http://fgcz-ms.uzh.ch/~cpanse/p1875/F255744.RData"))
# F255744 <- as.data.frame.mascot(F255744) 
# now available through ExperimentHub

library(ExperimentHub)
eh <- ExperimentHub(); 

load(query(eh, c("NestLink", "F255744.RData"))[[1]])

.ssrc.mascot(F255744, scores = c(10, 20, 40, 50), 
             pch = 16, 
             col = rgb(0.1,0.1,0.1,
                       alpha = 0.1)
)
```


# Session info

Here is the output of `sessionInfo()` on the system on which this
document was compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

# References

