<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{NestLink peptide barcode}
-->


---
title: "peptide_barcode (p1875)"
author: "Bernd Roschitzki & Christian Panse"
date: '2015-04-01, 2015-04-28,  2015-04-29, 2015-04-30, 2015-10-24'
output:
  slidy_presentation:
    keep_md: yes
  ioslides_presentation: default
  beamer_presentation: default
---

## Reqired R packages
[specL](http://dx.doi.org/10.1093/bioinformatics/btv105)
```{r}
if (packageVersion('specL') < '1.3.2')
{
  message("specL package version should be 1.3.2 or higher")
}
library(NestLink)
```

## Input
```{r}
aa_pool_x8 <- c(rep('A', 12), rep('S', 0), rep('T', 12), rep('N', 12), rep('Q', 12), rep('D', 8), 
              rep('E', 0), rep('V', 12), rep('L', 0), rep('F', 0), rep('Y', 8), rep('W', 0), 
              rep('G', 12), rep('P', 12))


aa_pool_1_2_9_10 <- c(rep('A', 8), rep('S', 7), rep('T', 7), rep('N', 6), rep('Q', 6), rep('D', 8), 
                      rep('E', 8), rep('V', 9), rep('L', 6), rep('F', 5), rep('Y', 9), rep('W', 6), 
                      rep('G', 15), rep('P', 0))

aa_pool_3_8 <- c(rep('A', 5), rep('S', 4), rep('T', 5), rep('N', 2), rep('Q', 2), rep('D', 8), 
                 rep('E', 8), rep('V', 7), rep('L', 5), rep('F', 4), rep('Y', 6), rep('W', 4), 
                 rep('G', 12), rep('P', 28))

```
---

## TEST
```{r}
table(aa_pool_x8)
length(aa_pool_x8)
table(aa_pool_1_2_9_10)
length(aa_pool_1_2_9_10)
table(aa_pool_3_8)
length(aa_pool_3_8)
```
---

## Compose a GPGXXXXXXXX(VR|VSR|VFGIR|VSGER) peptide
```{r}

replicate(10, compose_GPGx8cTerm(pool=aa_pool_x8))
```
---

## Compose a GPYYXXXXXXYYR peptide
```{r}  

compose_GPx10R(aa_pool_1_2_9_10, aa_pool_3_8)
```
---

## Generate peptides
```{r}
set.seed(2)

(sample.size <- 3E+04)

peptides.GPGx8cTerm <- replicate(sample.size, compose_GPGx8cTerm(pool=aa_pool_x8))
peptides.GPx10R <- replicate(sample.size, compose_GPx10R(aa_pool_1_2_9_10, aa_pool_3_8))
#write.table(peptides.GPGx8cTerm, file='/tmp/pp.txt')

```
---

## Compute peptide mass
```{r}
(smp.peptide <- compose_GPGx8cTerm(aa_pool_x8))
parentIonMass(smp.peptide)

pim.GPGx8cTerm <- unlist(lapply(peptides.GPGx8cTerm, function(x){parentIonMass(x)}))
pim.GPx10R <- unlist(lapply(peptides.GPx10R, function(x){parentIonMass(x)}))
pim.iRT <-  unlist(lapply(as.character(iRTpeptides$peptide), function(x){parentIonMass(x)}))

```
---

## Draw parent ion mass histogram
```{r}
(pim.min <- min(pim.GPGx8cTerm, pim.GPx10R))
(pim.max <- max(pim.GPGx8cTerm, pim.GPx10R))

(pim.breaks <- seq(round(pim.min - 1) , round(pim.max + 1) , length=75))

hist(pim.GPGx8cTerm, breaks=pim.breaks, probability = TRUE, 
     col='#1111AAAA', xlab='peptide mass [Dalton]', ylim=c(0, 0.006))
hist(pim.GPx10R, breaks=pim.breaks,
     probability = TRUE, add=TRUE, col='#11AA1188')
abline(v=pim.iRT, col='grey')
legend("topleft", c('GPGx8cTerm', 'GPx10R', 'iRT'),  fill=c('#1111AAAA', '#11AA1133', 'grey'))
``` 
---

## Compute hydrophobicity value

the specL::ssrc model is an implementation of [Krokhin, O. V. et al.](http://www.ncbi.nlm.nih.gov/pubmed/15238601)
```{r}
# just apply ssrc to a real world LC-MS run
ssrc <- unlist(lapply(peptideStd, function(x){specL:::ssrc(x$peptideSequence)}))
rt <- unlist(lapply(peptideStd, function(x){x$rt}))
plot(ssrc, rt); abline(ssrc.lm <- lm(rt ~ ssrc), col='red'); 
legend("topleft", paste("spearman", round(cor(ssrc, rt, method='spearman'),2)))
```

--- 

## Compute hydrophobicity value (cont)
```{r}
hydrophobicity <- function(x){unlist(lapply(x, specL::ssrc))}
hyd.GPGx8cTerm <- hydrophobicity(peptides.GPGx8cTerm)
hyd.GPx10R <- hydrophobicity(peptides.GPx10R)
hyd.iRT <- hydrophobicity(as.character(iRTpeptides$peptide))

(hyd.min <- min(hyd.GPGx8cTerm, hyd.GPx10R))
(hyd.max <- max(hyd.GPGx8cTerm, hyd.GPx10R))
hyd.breaks <- seq(round(hyd.min - 1) , round(hyd.max + 1) , length=75)
```
---

## Draw hydrophobicity histogram 

```{r}
hist(hyd.GPGx8cTerm, breaks = hyd.breaks, probability = TRUE, 
     col='#1111AAAA', xlab='hydrophobicity', 
     ylim=c(0, 0.06),
     main='Histogram')
hist(hyd.GPx10R, breaks = hyd.breaks, probability = TRUE, add=TRUE, col='#11AA1188')
  abline(v=hyd.iRT, col='grey')
legend("topleft", c('GPGx8cTerm', 'GPx10R', 'iRT'),  fill=c('#1111AAAA', '#11AA1133', 'grey'))
```
---

## QC of composed peptides
Input 
```{r}
round(table(aa_pool_x8)/length(aa_pool_x8), 2)

```
Output
```{r}
peptide2aa <- function(seq, from=4, to=4+8){
  unlist(lapply(seq, function(x){strsplit(substr(x, from, to), '')}))
}
peptides.GPGx8cTerm.aa <- peptide2aa(peptides.GPGx8cTerm)
round(table(peptides.GPGx8cTerm.aa)/length(peptides.GPGx8cTerm.aa), 2)
```
```{r}
peptides.GPx10R.aa <- peptide2aa(peptides.GPx10R, from=3, to=12)
round(table(peptides.GPx10R.aa)/length(peptides.GPx10R.aa), 2)
```

---

## Count GP patterns
```{r}
sample.size 

length(grep('^GP(.*)GP(.*)R$', peptides.GPGx8cTerm))

length(grep('^GP(.*)GP(.*)R$', peptides.GPx10R))
```

---

## Compute AA frequency table
count the peptides having the same AA composition
```{r}
sample.size 

table(table(tt<-unlist(lapply(peptides.GPGx8cTerm, 
  function(x){paste(sort(unlist(strsplit(x, ''))), collapse='')}))))
write.table(tt, file='/tmp/tt.txt')
table(table(unlist(lapply(peptides.GPx10R, 
  function(x){paste(sort(unlist(strsplit(x, ''))), collapse='')}))))
```

---


```{r}
par(mfrow=c(2, 2))
h <- NestLink:::.plot_in_silico_LCMS_map(peptides.GPGx8cTerm, main='GPGx8cTerm')
h <- NestLink:::.plot_in_silico_LCMS_map(peptides.GPx10R, main='GPx10R')
```

# Session information
```{r}
sessionInfo()
```